---
title: "Introduction to Rvest: Scraping Faculty Directories"
author: "Adam Garber"
date: "2024-02-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(tidyverse)
library(rvest)
library(robotstxt)
library(gt)
```


***

Example 1: University of Florida 

***

Check to see that the website allows scraping
```{r}

paths_allowed("https://arts.ufl.edu/directory/")

```

Read the html from the url address 
```{r}

page_uf <- read_html("https://arts.ufl.edu/directory/")

page_uf
```

## Search for names
```{r}
# Note: We have 350 names on this page!
page_uf %>% 
  html_nodes(".trigger .title")

```


```{r}

page_uf %>% 
  html_nodes(".trigger .title") %>% 
  html_text()

names <- page_uf %>% 
  html_nodes(".trigger .title") %>% 
  html_text()

```

## Search for emails

Check nodes: Data has what we need (but also some extra stuff...)
```{r}
# Note: Only 317 emails were extracted (uh oh!)
page_uf %>% 
  html_nodes("span:nth-child(1) a")
```

Check which attributes are available in the selected nodes with `html_attrs()`
```{r}
page_uf %>% 
  html_nodes("span:nth-child(1) a") %>% 
  html_attrs()
```

Select the desired attribute using `html_attr()`
```{r}
page_uf %>% 
  html_nodes("span:nth-child(1) a") %>% 
  html_attr("title")

```


```{r}
# Note: Only 317 emails were extracted (uh oh!)
emails <- page_uf %>% 
  html_nodes("span:nth-child(1) a") %>% 
  html_attr("title")

emails
```

## Search for positions
```{r}
positions <- page_uf %>% 
  html_nodes(".position") %>% 
  html_text()

positions
```


## Missing emails: hack off the bottom of the `df` (rows after 281 

Note: They are mostly professor emeriti or theater, arts, music faculty 
```{r}
email <- emails %>% head(281)
name <- names %>% head(281)
position <- positions %>% head(281)
```


## Create a `data.frame` for the UM directory 
```{r}
df_um <- tibble(
  order = 1:281,
  name = name,
  position = position,
  email = email) 
 
df_um %>% glimpse()
```


***

Example 2: Washington State University 

***

Read the html from the url address 
```{r}

url <- "https://everett.wsu.edu/paul-pitre/"

page <- read_html(url) 

```


## Search for names, postions, and emails 

```{r}
names <- page %>% 
  html_nodes(".wsu-c-article-header__title") %>% 
  html_text()

names
```

hmm, not exactly what we want...
```{r}
page %>% 
  html_nodes(".wsu-c-callout__title") %>% 
  html_text()
```

Let's try `html_text2()`
```{r}
positions <- page %>% 
  html_nodes(".wsu-c-callout__title") %>% 
  html_text2()

positions
```

## When the text is not in the right format (very common) use the `stringr` functions:
e.g., `str_remove(), str_replace(), str_subset(), str_squish(), str_c()...`

```{r}
page %>% 
  html_nodes("a:nth-child(3)") %>% 
  html_attr("href")

page %>% 
  html_nodes("a:nth-child(3)") %>% 
  html_attr("href") %>% 
  str_remove("mailto:")

emails <- page %>% 
  html_nodes("a:nth-child(3)") %>% 
  html_attr("href") %>% 
  str_remove("mailto:")
  
emails
```




## Create the data.frame combining each variable
```{r}
df_wsu <- tibble(
  name = names,
  email = emails,
  position = positions, 
  url = url
)

df_wsu
```

## Create a function
```{r}

scrape_page <- function(url){

 page <- read_html(url)   
 
 names <- page %>% 
   html_nodes(".wsu-c-article-header__title") %>% 
   html_text()

 positions <- page %>% 
   html_nodes(".wsu-c-callout__title") %>% 
   html_text2()

 emails <- page %>% 
   html_nodes("a:nth-child(3)") %>% 
   html_attr("href") %>% 
   str_remove("mailto:")
  
 df_wsu <- tibble(
   name = names,
   email = emails,
   position = positions, 
   url = url)
}

scrape_page(url = "https://everett.wsu.edu/paul-pitre/") %>% 
  glimpse()

```

## Read in the list of profile page URLs
```{r}

read_html("https://everett.wsu.edu/faculty-staff-directory/") %>% 
  html_nodes(".wsu-c-card__heading-link")
  
read_html("https://everett.wsu.edu/faculty-staff-directory/") %>% 
  html_nodes(".wsu-c-card__heading-link") %>% 
  html_attrs() 

all_pages <- read_html("https://everett.wsu.edu/faculty-staff-directory/") %>% 
  html_nodes(".wsu-c-card__heading-link") %>% 
  html_attr("href") 

all_pages
```


## Iterate using `map_dfr()` - Scrape 48 faculty profile pages
```{r}

wsu_directory <- map_dfr(all_pages, scrape_page)

wsu_directory %>% gt()

```



